SFJ: An implementation of Semantic Featherweight Java

### 2020-02-18 conference/paper.tex
use lncs template, get started on paper

\documentclass[10pt,a4paper,twocolumn]{article}

\usepackage[cm]{fullpage}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[hyphens]{url}
\usepackage{minted}
\usepackage[english]{babel}
\usepackage{cite}

\title{JSF}
\author{Artem Usov}
\date{February 2020}

@@

@@

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\title{SFJ: An implementation of Semantic Featherweight Java}
%\titlerunning{Abbreviated paper title}

\author{Artem Usov \and Ornela Dardha\orcidID{0000-0001-9927-7875}}

%\authorrunning{F. Author et al.}

\institute{School of Computing Science, University of Glasgow, United Kingdom \\
    \email{\{artem.usov, ornela.dardha\}@@glasgow.ac.uk}}

@@

\begin{abstract}
    The abstract should briefly summarize the contents of the paper in 15--250 words.

    \keywords{nominal and structural subtyping  \and Featherweight Java 
    \and object-oriented languages \and semantic subtyping \and type theory.}
\end{abstract}

@@

A typing system for a programming language is a set of deduction rules that allow

\begin{equation}
    \tau ::= \alpha \mid \mu
\end{equation}

Since we want our types to represent sets of values, we restrict our types to finite trees whose 
leaves are constants with no cycles. For example a recursive type $\alpha = [a : \alpha]$ would
be an infinite tree \textbf{new} $C$(\textbf{new} $C$($\cdots{}$)). Similarly the types $\alpha = 
[b: \beta]$, $\beta = [a = \alpha]$ would also be impossible to instantiate.

Therefore, to not allow this, when processing the AST of a program, we do not allow the type of 
the class we are defining to be a field and we mark any classes with only basic types in it's fields
as \textit{resolved} and otherwise if it contains a class type, we mark it as \textit{unresolved}. 
After processing the whole AST, we perform the following algorithm to decide whether the type 
definitions in the program are valid.

\begin{verbatim}
boolean resolutionOccured = false
do 
    for each class that is unresolved:
        boolean resolved = true

        for each field that is a class type:
            if class type is not resolved 
                resolved = false

        if resolved == true
            set class to be resolved
            resolutionOccured = true
while resolutionOccured == true

if not all classes are resolved
    program contains invalid type definition
\end{verbatim}

\subsubsection{Sample Heading (Third Level)}
Only two levels of headings should be numbered. Lower level headings remain unnumbered; they are 
formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of headings. Table~\ref{tab1} gives a 
summary of all heading levels.

\begin{table}
    \caption{Table captions should be placed above the tables.}
    \label{tab1}
    \begin{tabular}{|l|l|l|}
        \hline
        Heading level     & Example                                          & Font size and style \\
        \hline
        Title (centered)  & {\Large\bfseries Lecture Notes}                  & 14 point, bold      \\
        1st-level heading & {\large\bfseries 1 Introduction}                 & 12 point, bold      \\
        2nd-level heading & {\bfseries 2.1 Printing Area}                    & 10 point, bold      \\
        3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold      \\
        4th-level heading & {\itshape Lowest Level Heading.} Text follows    & 10 point, italic    \\
        \hline
    \end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separateline.

\begin{equation}
    x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and schemas. Whenever possible, use 
vector graphics instead.

%\begin{figure}
%   \includegraphics[width=\textwidth]{fig1.eps}
%  \caption{A figure caption is always placed below the illustration.
%     Please note that short captions are centered, while long ones are
%     justified by the macro package automatically.} \label{fig1}
%\end{figure}

\begin{theorem}
    This is a sample theorem. The run-in heading is set in bold, while
    the following text appears in italics. Definitions, lemmas,
    propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
    Proofs, examples, and remarks have the initial word in italics,
    while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{Dardha2017}.

\bibliographystyle{splncs04}
\bibliography{paper}
